---
graphics: yes
name: Anthony
surname: Schmidt
#headcolor: 01416f
#qualifications: 
position: "PhD Student and Data Visualization Researcher"
#address: ""
#phone: ""
www: anthonyschmidt.co
email: "aschmi11@utk.edu"
twitter: anthonyteacher
github: acircleda
aboutme:
date: '`r format(Sys.Date(), "%B %d, %Y")`'
csl: "csl/apa-cv.csl"
nocite: "@*"
knit: bookdown::render_book
bibliography_anthony_pub: "bib/anthony_pub.bib"
bibliography_anthony_preprints: "bib/anthony_preprint.bib"
bibliography_anthony_reviews: "bib/anthony_reviews.bib"
bibliography_anthony_tech: "bib/anthony_techreports.bib"
bibliography_anthony_other: "bib/anthony_other.bib"
bibliography_anthony_conf_intl: "bib/anthony_conf_intl.bib"
bibliography_anthony_conf_regional: "bib/anthony_conf_regional.bib"
bibliography_anthony_conf_posters: "bib/anthony_conf_posters.bib"
bibliography_anthony_conf_talks: "bib/anthony_conf_talks.bib"
bibliography_anthony_conf_invited: "bib/anthony_conf_invited.bib"
bibliography_anthony_conf_workshops: "bib/anthony_conf_workshops.bib"
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(RefManageR)
RefManageR::BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           sorting = "ydnt",
           cite.style = "alphabetic",
           style = "markdown",
#           hyperlink = FALSE,
           dashed = FALSE)

library(vitae)
library(tidyverse)
library(gsheet)
library(gt)
```

<!--chapter:end:index.Rmd-->

# Education

```{r education}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1760172285") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what = Degree,
                          when = Year,
                          with = Institution, 
                          where = Location, 
                          why)
```

<!--chapter:end:docs/education.Rmd-->

# Professional Appointments

```{r working-experience}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1554751840") %>%
  vitae::detailed_entries(with = title, 
                          when = date, 
                          what = institution, 
                          where = location)
```

<!--chapter:end:docs/working_exp.Rmd-->

# Publications

## Peer Reviewed Journal Articles

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_anthony_pub}
:::
\endgroup

## Pre-Prints

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1558956454") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> preprints
  cat(paste(preprints), sep = '\n\n')

```


\endgroup


## Book Reviews

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_anthony_reviews}
:::
\endgroup

## Technical Reports

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- BibLaTeX Method (currently not working) -->
<!-- ::: {#refs_anthony_tech} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1473597883") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> tr
  cat(paste(tr), sep = '\n\n')

```

\endgroup

## Other Publications

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_anthony_other}
:::
\endgroup

# Conference Papers and Presentations

## International/National Conferences

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- ::: {#refs_anthony_conf_intl} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=318960497") %>%
  filter(category == "intl") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> intl
  cat(paste(intl), sep = '\n\n')

```

\endgroup

## Regional Conferences

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- ::: {#refs_anthony_conf_regional} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=318960497") %>%
  filter(category == "regional") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> regional
  cat(paste(regional), sep = '\n\n')

```

\endgroup

## Poster Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- ::: {#refs_anthony_conf_posters} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=318960497") %>%
  filter(category == "poster") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> poster
  cat(paste(poster), sep = '\n\n')

```


\endgroup

## Campus & Department Talks

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- ::: {#refs_anthony_conf_talks} -->
<!-- ::: -->


```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=318960497") %>%
  filter(category == "campus talk") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> campus
  cat(paste(campus), sep = '\n\n')

```


\endgroup

## Invited Talks

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- ::: {#refs_anthony_conf_invited} -->
<!-- ::: -->


```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=318960497") %>%
  filter(category == "invited") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> invited
  cat(paste(invited), sep = '\n\n')

```


\endgroup

## Professional Workshops, Webinars, and Trainings

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- ::: {#refs_anthony_conf_workshops} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=318960497") %>%
  filter(category == "workshops") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> workshops
  cat(paste(workshops), sep = '\n\n')

```


\endgroup

<!--chapter:end:docs/publication.Rmd-->

# Research and Evaluation Experience

```{r research-experience}
library(tidyverse)
library(gsheet)
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=144487203") %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(with = project,
                          when = date,
                          where = institution,
                          why = details)
```

<!--chapter:end:docs/research_exp.Rmd-->

# Teaching Experience
```{r teaching-experience}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=802976282") %>%
  filter(category=="teaching") %>%
  select(-category) %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(what = title, when = dates, with = school, where = location, details)
```


# Other Teaching Experience

```{r other-teaching-experience}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=802976282") %>%
  filter(category=="other teaching") %>%
  select(-category) %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(what = title, when = dates, with = school, where = location, details)
```

# Teacher Training Experience

```{r teacher-training-experience}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=802976282") %>%
  filter(category=="teacher training") %>%
  select(-category) %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(what = title, when = dates, with = school, where = location, details)
```

<!--chapter:end:docs/teaching_exp.Rmd-->

# Awards and Honors

```{r award}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1320047315") %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(what = organization,
                          when = date,
                          with = award_name,
                          why = details)
```

<!--chapter:end:docs/award.Rmd-->

# Current Memberships

```{r results='asis'}
membership <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1398743395") %>%
    pull(organization)
  cat(paste('-', membership), sep = '\n')

```


<!--chapter:end:docs/membership.Rmd-->

# Skills

\begin{cvskills}

```{r results='asis'}
skills <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=885656894") %>%
  mutate(category = paste0("{", category, "}"),
         details = paste0("{", details, "}"),
         skills = paste0("\\cvskill", "\n", category, "\n", details)) %>%
  pull(skills)

  cat(paste('', skills), sep = '\n')
```


\end{cvskills}

<!--chapter:end:docs/skills.Rmd-->

# Notes

This CV is reproducible. All the source code behind this CV is available on [my GitHub repo](https://github.com/acircleda/CV){target="_blank"}.

\

<!--chapter:end:docs/backmatter.Rmd-->

