---
graphics: yes
name: Sean Owen
surname: Clancy, Ph.D.
headcolor: 01416f
position: "Leader, Scientist, Technology Developer, Problem Solver"
www: seanclancy.org
email: "me@seanclancy.org"
twitter: seanclancy
github: seanclancy
linkedin: seanclancy
orcid: 0000-0002-3560-1469
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
header-includes:
  - \definecolor{linkscolor}{HTML}{026dbb}
  - \usepackage{caption}
  - \usepackage{colortbl}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{hyperref}
  - \arrayrulecolor{white}
  - \hypersetup{colorlinks=true, linkcolor=linkscolor, filecolor=linkscolor, urlcolor=linkscolor, urlbordercolor=linkscolor}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(gsheet)
library(gt)
library(flextable)
library(knitr)
library(kableExtra)
```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# Education

```{r education}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit#gid=1760172285") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what = Degree,
                          when = Year,
                          where = Institution, 
                          with = Location, 
                          why)
```


# Professional Appointments


```{r working-experience}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=1554751840") %>%
  vitae::detailed_entries(what = title, 
                          when = date, 
                          where = institution, 
                          with = location)
```

# Publications

## Peer Reviewed Journal Articles

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r peerreviewed, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=0") %>%
  filter(category == "peer-reviewed") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Clancy, S.", "**Clancy, S.**")) %>%
  pull(markdown) -> peer
  cat(paste(peer), sep = '\n\n')

```

\endgroup
\leavevmode\newline

## Pre-Prints and Unpublished Manuscripts

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r preprint, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=1558956454") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Clancy, S.", "**Clancy, S.**")) %>%
  pull(markdown) -> preprints
  cat(paste(preprints), sep = '\n\n')

```

\endgroup
\leavevmode\newline

## Technical Reports

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r techreports, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=1473597883") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Clancy, S.", "**Clancy, S.**")) %>%
  pull(markdown) -> tr
  cat(paste(tr), sep = '\n\n')

```

\endgroup
\leavevmode\newline

# Conference Papers and Presentations

## International/National Conferences

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}


```{r intlconf, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=318960497") %>%
  filter(category == "intl") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Clancy, S.", "**Clancy, S.**")) %>%
  pull(markdown) -> intl
  cat(paste(intl), sep = '\n\n')

```

\endgroup
\leavevmode\newline

## Regional Conferences

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r regional, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=318960497") %>%
  filter(category == "regional") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Clancy, S.", "**Clancy, S.**")) %>%
  pull(markdown) -> regional
  cat(paste(regional), sep = '\n\n')

```

\endgroup
\leavevmode\newline

## Poster Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}


```{r poster, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=318960497") %>%
  filter(category == "poster") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Clancy, S.", "**Clancy, S.**")) %>%
  pull(markdown) -> poster
  cat(paste(poster), sep = '\n\n')

```


\endgroup
\leavevmode\newline


## Invited Talks

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r invited, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=318960497") %>%
  filter(category == "invited") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Clancy, S.", "**Clancy, S.**")) %>%
  pull(markdown) -> invited
  cat(paste(invited), sep = '\n\n')

```


\endgroup
\leavevmode\newline

## Professional Workshops, Webinars, and Trainings

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r workshops, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=318960497") %>%
  filter(category == "workshops") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Clancy, S.", "**Clancy, S.**")) %>%
  pull(markdown) -> workshops
  cat(paste(workshops), sep = '\n\n')

```


\endgroup
\leavevmode\newline


# Research and Evaluation Experience

```{r research-experience}
library(tidyverse)
library(gsheet)
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=144487203") %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(what = project,
                          when = date,
                          where = institution,
                          why = details)
```


# Teaching Experience

## Full-Time Experience

```{r teaching-experience}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=802976282") %>%
  filter(category=="teaching") %>%
  select(-category) %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(where = title, when = dates, what = school, with = location, details)
```


## Other Teaching Experience

```{r other-teaching-experience}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=802976282") %>%
  filter(category=="other teaching") %>%
  select(-category) %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(where = title, when = dates, what = school, with = location, details)
```

# Awards and Honors

```{r award}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=1320047315") %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(where = organization,
                          when = date,
                          what = award_name,
                          with = details)
```

# Skills

\vspace*{-\baselineskip}

```{r skills, message=FALSE, warning=FALSE}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit#gid=885656894") %>%
  mutate(category = ifelse(is.na(category), " ", category),
         details = ifelse(is.na(details), " ", details
         )) %>%
  knitr::kable(col.names = NULL, align=c("l","l"), escape = F) %>%
  kableExtra::row_spec(row=2, extra_latex_after = "\\arrayrulecolor{white}") %>%
  kableExtra::column_spec(column = 1, bold = T)
```


\leavevmode\newline

# Memberships

```{r results='asis'}
membership <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit?pli=1#gid=1398743395") %>%
    pull(organization)
  cat(paste('-', membership), sep = '\n')

```
\clearpage
\pagebreak

# Skills

```{r skills, message=FALSE, warning=FALSE}
  options(width = 60)
gsheet2tbl("https://docs.google.com/spreadsheets/d/1iwBWh1LUKUks0MBuS7vU8L0m35Qv70sb3Aa-84ybYBo/edit#gid=885656894") %>%
  mutate(category = ifelse(is.na(category), " ", category),
         details = ifelse(is.na(details), " ", details
         )) %>%
  knitr::kable(col.names = NULL, align=c("l","l"), escape = F, booktabs = T) %>%
  kableExtra::row_spec(row=2, extra_latex_after = "\\arrayrulecolor{white}") %>%
  kableExtra::kable_styling(full_width = F, latex_options = c("striped", "scale_down")) %>%
  kableExtra::column_spec(column = 1, bold = T, width="1.75in") %>%
  kableExtra::column_spec(column = 2, width = "5in")
```
