# Publications

## Peer Reviewed Journal Articles

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_anthony_pub}
:::
\endgroup

## Pre-Prints and Unpublished Manuscripts

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1558956454") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> preprints
  cat(paste(preprints), sep = '\n\n')

```


\endgroup


## Book Reviews

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_anthony_reviews}
:::
\endgroup

## Technical Reports

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- BibLaTeX Method (currently not working) -->
<!-- ::: {#refs_anthony_tech} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1473597883") %>%
  select(markdown) %>%
  slice(-1:-6) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> tr
  cat(paste(tr), sep = '\n\n')

```

\endgroup

# Conference Papers and Presentations

## International/National Conferences

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- ::: {#refs_anthony_conf_intl} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=318960497") %>%
  filter(category == "intl") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  slice(-2) %>%
  pull(markdown) -> intl
  cat(paste(intl), sep = '\n\n')

```

\endgroup

## Regional Conferences

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- ::: {#refs_anthony_conf_regional} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=318960497") %>%
  filter(category == "regional") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  slice(-4, -5) %>%
  pull(markdown) -> regional
  cat(paste(regional), sep = '\n\n')

```

\endgroup

## Poster Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- ::: {#refs_anthony_conf_posters} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=318960497") %>%
  filter(category == "poster") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  slice(-3) %>%
  pull(markdown) -> poster
  cat(paste(poster), sep = '\n\n')

```

# Software

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1692561333") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> software
  cat(paste(software), sep = '\n\n')

```


\endgroup
