---
graphics: yes
name: Anthony
surname: Schmidt
headcolor: 01416f
position: "Data Science & Applied Research"
www: anthonyschmidt.co
email: "aschmi11@utk.edu"
twitter: anthonyteacher
github: acircleda
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
header-includes:
  - \definecolor{linkscolor}{HTML}{026dbb}
  - \usepackage{caption}
  - \usepackage{hyperref}
  - \usepackage{colortbl}
  - \arrayrulecolor{white}
  - \hypersetup{colorlinks=true, linkcolor=linkscolor, filecolor=linkscolor, urlcolor=linkscolor, urlbordercolor=linkscolor}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(gsheet)
library(gt)
library(flextable)
```

I have a passion for data analysis, statistics, and visualization. I have both graduate training and full-time work experience with applied statistics, psychometrics, and data viz. I eat, breathe, and sleep R. I am looking for an opportunity to apply these skills and push myself to learn more!

# Education


```{r education}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1760172285") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what = Degree,
                          when = Year,
                          where = Institution, 
                          with = Location, 
                          why,
                          .protect = FALSE)
```

# Professional Appointments


```{r work}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=161085706") %>%
tidyr::fill(-why) %>%
  vitae::detailed_entries(what = title,
                          when = date,
                          where = institution,
                          why = why,
                          .protect = F)
```

# Software
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r software, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1692561333") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> software
  cat(paste(software), sep = '\n\n')

```


\endgroup
\leavevmode\newline

# Selected Publications and Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}


```{r results='asis'}
rbind(
    gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=0") %>%
  filter(category == "peer-reviewed") %>%
    select(year, markdown),
  gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1473597883") %>%
    slice(1:3) %>%
    select(year, markdown)
) %>%
  arrange(-year) %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  slice(1,2,15,6) %>%
  pull(markdown) -> intl
  cat(paste(intl), sep = '\n\n')

```
# Skills

\vspace*{-\baselineskip}

```{r skills, message=FALSE, warning=FALSE}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=885656894") %>%
  mutate(category = ifelse(is.na(category), " ", category),
         details = ifelse(is.na(details), " ", details
         )) %>%
  knitr::kable(col.names = NULL, align=c("l","l"), escape = F) %>%
  kableExtra::row_spec(row=2, extra_latex_after = "\\arrayrulecolor{white}") %>%
  kableExtra::column_spec(column = 1, bold = T)
```


\leavevmode\newline


# Notes

This CV is reproducible. All the source code behind this CV is available on \href{https://github.com/acircleda/CV}{my Github repo}.
